---
title: "Candace Lee Savonen"
output:   
  prettydoc::html_pretty:
    theme: cayman
---

**Current Position:** Biological Data Analyst for [Childhood Cancer Data Lab](https://www.ccdatalab.org/)  
**Phone:** 734 735 2469  
**Website:** [cansavvy.com](https://cansavvy.com)  
**GitHub:** [cansavvy](https://github.com/cansavvy)  
**Email:** cansav09@gmail.com  
**Last Update:** `r format(Sys.time(), '%B %Y')`  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Specific established skills

- Processing of gene expression data - Microarray and RNA-Seq (including [Single-cell](https://github.com/AlexsLemonade/scRNA-seq_sandbox))
- R programming including [Bioconductor, Tidyverse, and RMarkdown](https://github.com/AlexsLemonade/refinebio-examples)
- [Genomic data mining](https://github.com/cansavvy/sample-code/blob/master/experiment_accession_retrieval.R)
- Molecular neurobiology
- Making [bioinformatics educational materials](https://github.com/AlexsLemonade/training-modules/tree/master/intro-to-R-tidyverse) and other [bioinformatics examples](https://github.com/AlexsLemonade/refinebio-examples)
- Evaluating [single nucleotide variant datasets](https://github.com/AlexsLemonade/OpenPBTA-analysis/tree/master/analyses/snv-callers)

# Broader skills 

- Learns new data types and methods efficiently
- Good at working as a part of a team
- Welcomes and incorporates constructive feedback

# Education

```{r}
# Make education history table
edu <- tibble::tribble(~Degree, ~ Year, ~ Institution, ~ Where,
  "Masters of Neuroscience", "2015 - 2018", "Michigan State University", "East Lansing, MI",
  "Bachelors of Science - Psychology/Biology", "2009 - 2013", "Oakland University", "Rochester Hills, MI",
  "Associate of Science", "2005 - 2009 ", "Monroe County Community College", "Monroe, MI"
)
# Adjust style
edu <- knitr::kable(edu, "html") %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::column_spec(2, "10em")

# Print this
edu
```

# Work History

```{r}
edu <- tibble::tribble(~Title, ~ Year, ~ Institution, ~ Where,
  "Biological Data Analyst", "2018 - Current", "Childhood Cancer Data Lab", "Philadelphia, PA",
  "Research Assistant ", "2013 - 2015", "Wayne State School of Medicine, Pharmacology", "Detroit, MI",
)
# Print this
edu <- knitr::kable(edu, "html") %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::column_spec(2, "10em")

edu
```

# Publications

[Google Scholar page](https://scholar.google.com/citations?user=zcRmG_UAAAAJ&hl=en) has links to all publications.

```{r}
# Set up publications 
pubs <- scholar::get_publications("zcRmG_UAAAAJ&hl=en") %>%
  dplyr::select(-cites, -cid, -number, -pubid) %>%
  dplyr::rename_all(toupper) %>% 
  dplyr::arrange(desc(YEAR)) %>% 
  dplyr::mutate(AUTHOR = gsub("CL Savonen|C Savonen", " **C Savonen** ", AUTHOR),
                JOURNAL =c(as.character(JOURNAL[1:6]), "Oakland Univ. Honors College Thesis"), 
                TITLE = gsub("RNA s", "RNAs", TITLE),
                )

# Make it a pretty table
pubs <- knitr::kable(pubs, "html") %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::column_spec(3:4, "5em") 

# Print it out
pubs
```

# Fun Facts
- She [swam Division I NCAA for Oakland University (was team captain)](https://www.collegeswimming.com/swimmer/90314/).
- She ran a Marathon (the Disney marathon).
- She has two mixed breed rescue dogs with her husband, Jon. 
