---
title: "Candace Lee Savonen."
output:   
  prettydoc::html_pretty:
    theme: lumen
---

**Current Position:** Biological Data Analyst for [Childhood Cancer Data Lab](https://www.ccdatalab.org/)  
**Phone:** 734 735 2469  
**Website:** [cansav09.com](cansav09.com)  
**GitHub:** [cansav09](https://github.com/cansav09)  
**Email:** cansav09@gmail.com  
**Last Update:** `r format(Sys.time(), '%B %Y')`  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Skills

- Processing of gene expression data - microarray and RNA-Seq (including [single-cell](https://github.com/AlexsLemonade/scRNA-seq_sandbox))
- R programming including [Bioconductor, Tidyverse, and RMarkdown](https://github.com/AlexsLemonade/refinebio-examples)
- [Genomic data mining](https://github.com/cansav09/sample-code/blob/master/experiment_accession_retrieval.R)
- Molecular neurobiology
- Making [bioinformatics educational materials](https://github.com/AlexsLemonade/training-modules/tree/master/intro-to-R-tidyverse) and other [bioinformatics examples](https://github.com/AlexsLemonade/refinebio-examples)
- Analyzing [single nucleotide variant data](https://github.com/AlexsLemonade/OpenPBTA-analysis/tree/master/analyses/snv-callers)

# Education

```{r}
edu <- tibble::tribble(~Degree, ~ Year, ~ Institution, ~ Where,
    "Masters of Neuroscience", "2015 - 2018", "Michigan State University", "East Lansing, MI",
    "Bachelors of Science - Psychology/Biology", "2009 - 2013", "Oakland University", "Rochester Hills, MI",
    "Associate of Science", "2005 - 2009 ", "Monroe County Community College", "Monroe, MI"
)
# Print this
edu <- knitr::kable(edu, "html") %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::column_spec(2, "10em")

edu
```

# Work History

```{r}
edu <- tibble::tribble(~Title, ~ Year, ~ Institution, ~ Where,
  "Biological Data Analyst", "2018 - Current", "Childhood Cancer Data Lab", "Philadelphia, PA",
  "Research Assistant ", "2013 - 2015", "Wayne State School of Medicine, Pharmacology", "Detroit, MI",
)
# Print this
edu <- knitr::kable(edu, "html") %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::column_spec(2, "10em")

edu
```

# Publications

```{r}
pubs <- scholar::get_publications("zcRmG_UAAAAJ&hl=en") %>%
  dplyr::select(-cites, -cid) %>%
  dplyr::rename_all(toupper) %>% 
  dplyr::arrange(desc(YEAR))

pubs <- knitr::kable(pubs, "html") %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::column_spec(3:6, "5em") 

pubs
```

# Fun facts
- She has spent way too much time on making a trivia quiz all about the state of Michigan.
- She swam Division I NCAA for Oakland University (was team captain).
- She ran a Marathon (the Disney marathon).
- Her fiancé Jon and her have two dogs named Eevee and Jäger, both are mixed breed rescues that are quirky.

